---
output:
    pdf_document:
        dev: cairo_pdf
        latex_engine: xelatex
        fig_caption: yes
header-includes:
- \usepackage{titling}
- \setlength{\droptitle}{10em}
- \renewcommand{\caption}{}
- \usepackage[font=bf]{caption}
- \pagenumbering{gobble}
---

```{r dependencies, include=FALSE}
library("ggplot2")
library(cowplot)
library("dplyr")
library("survival")
library("knitr")
library("gridExtra")
library("tidyr")
library("kableExtra")
library("data.table")
options(warn=-1)
opts_chunk$set(dpi=300)
```

```{r echo= F}

d= fread(snakemake@input[[1]], h=T)
x= sum(as.numeric(readLines(snakemake@input[[2]])))

d= filter(d, pvalue< 0.05/x)

d= d[order(d$pvalue, decreasing=F),]

d$Estimate= round((exp(d$beta)- 1) * 100, 1)
d$lowerci= round((exp(d$beta - 1.96 * d$sd) -1) * 100, 1)
d$upperci= round((exp(d$beta + 1.96 * d$sd) -1) * 100, 1)
d$beta= round(d$beta,3)
d$sd= round(d$sd, 3)
d$pos= as.integer(d$pos)
d$chr= as.integer(d$chr)
d$variant= paste(d$chr, d$pos, d$REF, d$EFF, sep= ':')
d$Estimate= paste0(d$Estimate, ' (', d$lowerci, ', ', d$upperci, ')')

d= select(d, variant, n, het, hom, beta, sd, Estimate, pvalue, gene, Mim)

kable(d, align= c('l', 'c', 'c', 'c', 'c', 'c', 'c', 'c', 'c', 'c'), row.names= F, col.names=c('Chr:pos:REF:EFF', 'n', 'n heterozygous', 'n homozygous', 'Beta', 'Standard Error', 'Estimate (95% CI)', 'P-value', 'Gene', 'OMIM'), caption = "S5 Table: Maternal genetic variants within high and low confidence segments associated with time-to-spontaneous onset of delivery under a recessive model.", booktabs = T) %>% kable_styling(latex_options= c('striped', 'scale_down')) %>% column_spec(1, bold = T, color = "black", background = "white") %>% footnote(general_title= '', general= c('Only genetic variants passing a relaxed Bonferroni correction (0.05/ 580 tested variants) are shown. For each segment, the closest protein-coding gene is also shown, and for this gene, the Mim phenotype number for a phenotype with recessive inheritance. The total number of genetic variants tested was 580. AFT model was adjusted for sub-cohort, the first 10 PC, parity, and autozygosity (FROH).', 'The effect size reflects the effect of the autozygous segment on time-to-spontaneous onset of delivery, representing the percent difference in time-to-spontaneous onset of delivery between subjects affected by an autozygous segment in the region vs those not affected. '), threeparttable= T)
